\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{PS1 Zhang}
\author{Haotian Zhang}

\begin{document}
\maketitle

\section{Introduction}

I am a first-year Ph.D. student in the department of Marketing and Supply Chain Management. 

After I got my Bachelor degree from Nanjing Audit University, China in Finance, I worked in an auditing firm for a year. During this period, I felt that auditing, which transforms boring accounting statements into annual reports that are easier for people to understand, is a very interesting job. I discovered my own interest in analyzing data and turning them into compelling stories. But I was not very good at reading accounting statements and after discussing it with my family, they introduced me to a new major, business analysis. So I went to the University of Pittsburgh and got my Master degree in Finance and Business Analytics there. 

For this course, I hope to learn some methods for analyzing data and some perspectives of interpreting data from an economist's perspective. I will strive to become a data scientist who can tell stories to everyone by analyzing data in the future.

For my project for this class, I would like to introduce to you a subculture economic phenomenon. This phenomenon is called the "Guzi Economy" in China. "Guzi" is the transliteration of the English word "Goods", comes from the two-dimensional culture, which refers to IP-related products such as comics, animations, and games, such as badges, cards, and pendants, which reflects that the younger generation is willing to pay for "emotional value". This project has its challenges. For example, since 2024 is known as the first year of the "Guzi Economy", I doubt whether I can collect sufficiently representative or convincing data to analyze such an economic phenomenon. 

\section{Equation}

\[ a^2 + b^2 = c^2 \]



\end{document}